\def\basedir{psava/gpgn302}

\blue{
  \sidebar{
    \section{Setup}
    \begin{itemize}
    \item Source your \texttt{.bashrc} file to make sure that you have
      all your environment variables set:\\
      \texttt{source $\sim$/.bashrc}
    \item Change to the class directory:\\
      \texttt{cd $\sim$/gpgn302}
    \item Copy the current lab:\\
      \texttt{cp -r $\sim$\basedir/\thisdoc \; .} \\
      Mind the dot at the end of the command.
    \item Change to the lab directory:\\
      \texttt{cd \thisdoc}
    \item Open the file \texttt{paper.tex} with your favorite text
      editor and put your name at the top of the file in the \LaTeX~
      variable named \texttt{author}.
    \item Change to the example directories which could be either one
      of the names listed below:\\
      \texttt{cd \exedirs}
    \item Make a directory for your figures:\\
      \texttt{mkdir /tmp/\$USER} \\
      The variable \texttt{\$USER} is your username. \\
      Make a symbolic link to your temp figure directory (repeat for
      every example):\\
      \texttt{ln -s /tmp/\$USER Fig} \\
      This means that your figures which go into \texttt{Fig} actually
      go to \texttt{/tmp/\$USER}. In this way, you do not fill your
      home directory which has a pretty small disk quota.
    \item In a terminal, build and view all figures by running: \\
      \texttt{scons view} \\
      Once a figure pops-up on screen, close it by pressing
      \texttt{Q}. Make sure that your NumLock key is not
      pressed. \texttt{scons} will then move to the next target. If
      you would like to build an individual figure called
      \texttt{myfig}, run \\
      \texttt{scons myfig.view} 
    \item Modify the \texttt{SConstruct} as outlined in the
      assignment. Repeat your figure builds to see how the changes to
      the setup impact the figures.
    \item Check all the results to make sure that they are ok. You can
      do this either by typing \\
      \texttt{scons view} \\
      to see all the results in the order in which they are listed in the
      \texttt{SConstruct} or by typing \\
      \texttt{xtpen Fig/myfig.vpl} \\
      where \texttt{myfig} is a specific figure you have created. You can
      also visualize figures whose name follow a specific pattern with the
      command \\
      \texttt{xtpen Fig/myfig*.vpl}
    \end{itemize}
  }
}
